### 2007-01-15 Documentation/Paper2/paper2.tex
*** empty log message ***

\begin{table}[t!]
{\small
\begin{center}
\begin{tabular}{llp{7.0cm}c}
\hline
Experiment & Filename & Short description &  \Refs \\
\hline 
\multicolumn{4}{l}{\underline{Superbeam experiments:}} \\
T2K & {\tt T2K.glb} & J-PARC to Super-Kamiokande &  \cite{Itow:2001ee,Huber:2002mx} \\
T2HK & {\tt T2HK.glb} & J-PARC to Hyper-Kamiokande &  \cite{Itow:2001ee,Huber:2002mx} \\
NO$\nu$A & {\tt NOvA.glb} & Fermilab NuMI beamline off-axis  & \cite{Ambats:2004js,Yang_2004} \\
SPL & {\tt SPL.glb} & CERN to Fr\'{e}jus & \cite{Campagne:2006yx,Campagne:2004wt,Mezzetto:2003mm} \\[0.2cm]
\multicolumn{4}{l}{\underline{Reactor experiments:}} \\
{\sc Reactor-I} & {\tt Reactor1.glb} & Small reactor exp., 
$\mathcal{L} = 400 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$
& \cite{Huber:2003pm} \\
{\sc Reactor-II} & {\tt Reactor2.glb} & Large reactor exp., 
$\mathcal{L} = 8\, 000 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$ 
& \cite{Huber:2003pm} \\
Double{\sc Chooz} & {\tt D-Chooz\_near.glb} & Double Chooz near 
detector & \cite{Huber:2006vr} \\ 
 & {\tt D-Chooz\_far.glb} & Double Chooz far detector & \\[0.2cm]
\multicolumn{4}{l}{\underline{$\beta$-Beams:}} \\
Low $\gamma$ & {\tt BB\_100.glb} & $\gamma=100$ CERN to Fr\'{e}jus 
scenario & \cite{Campagne:2006yx} \\
Medium $\gamma$ & {\tt BB\_350.glb} & $\gamma=350$ green field scenario 
& \cite{Burguet-Castell:2005pa} \\
Variable $\gamma$ & {\tt BBvar\_WC.glb} & Variable $\gamma$ beta beam with water Cherenkov detector, $50 \lesssim \gamma \lesssim 500$ & \cite{Huber:2005jk} \\[0.2cm]
	& {\tt BBvar\_TASD.glb} & Variable $\gamma$ beta beam with totally active scint. detector (TASD), 
$100 \lesssim \gamma \lesssim 3\, 000$ & \cite{Huber:2005jk} \\[0.4cm]
\multicolumn{4}{l}{\underline{Neutrino factories:}} \\
Standard & {\tt NFstandard.glb} & Standard neutrino factory, $50 \, \mathrm{kt}$ magnetized iron calorimeter, 
$E_\mu = 50 \, \mathrm{GeV}$ & \cite{Huber:2002mx} \\
Variable $E_\mu$ & {\tt NFvar.glb} & Variable neutrino factory, disapp. channels
{\em without} CID; $10 \, \mathrm{GeV} \lesssim E_\mu \lesssim 80 \, \mathrm{GeV}$ & \cite{Huber:2002mx,Huber:2006wb}  \\
Gold + Silver & {\tt NF\_GoldSilver.glb} & As {\tt NFvar.glb} 
plus 5~kt ECC detector for Silver Channel
measurement & \cite{Huber:2002mx,Huber:2006wb,Autiero:2003fu} \\
Hybrid detector & {\tt NF\_hR\_lT.glb} & As {\tt NFvar.glb}, but 
lower threshold and better energy resolution & \cite{Huber:2002mx,Huber:2006wb} \\
\hline
\end{tabular}
\end{center}
} % small
\mycaption{\label{tab:experiments} 
Pre-defined experiment prototypes coming with \GLOBESN : The columns represent the \AEDL\ filename, 
a short description, and the references in which they are originally used and 
discussed (except from minor modifications, such as a different implementation of 
the energy threshold function). 
%
IS THE GAMMA=350 OPTION REALLY GREEN-FIELD? I THOUGHT THAT THIS MAY BE THE MAXIMUM
ONE COULD GET OUT OF THE SPS WITH ACCELERATOR MODIFICATIONS? [WW]
}
\end{table}

>>>>

\begin{table}[t!]
{\small
\begin{center}
\begin{tabular}{llp{7.0cm}c}
\hline
Experiment & File name & Short description &  \Refs \\
\hline 
\multicolumn{4}{l}{\underline{Superbeam experiments:}} \\
T2K & {\tt T2K.glb} & J-PARC to Super-Kamiokande &  \cite{Itow:2001ee,Huber:2002mx} \\
T2HK & {\tt T2HK.glb} & J-PARC to Hyper-Kamiokande &  \cite{Itow:2001ee,Huber:2002mx} \\
NO$\nu$A & {\tt NOvA.glb} & Fermilab NuMI beamline off-axis  & \cite{Ambats:2004js,Yang_2004} \\
SPL & {\tt SPL.glb} & CERN to Fr\'{e}jus & \cite{Campagne:2006yx,Campagne:2004wt,Mezzetto:2003mm} \\[0.2cm]
\multicolumn{4}{l}{\underline{Reactor experiments:}} \\
{\sc Reactor-I} & {\tt Reactor1.glb} & Small reactor exp., 
$\mathcal{L} = 400 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$
& \cite{Huber:2003pm} \\
{\sc Reactor-II} & {\tt Reactor2.glb} & Large reactor exp., 
$\mathcal{L} = 8\, 000 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$ 
& \cite{Huber:2003pm} \\
Double{\sc Chooz} & {\tt D-Chooz\_near.glb} & Double Chooz near 
detector & \cite{Huber:2006vr} \\ 
 & {\tt D-Chooz\_far.glb} & Double Chooz far detector & \\[0.2cm]
\multicolumn{4}{l}{\underline{Beta beams:}} \\
Low $\gamma$ & {\tt BB\_100.glb} & $\gamma=100$ CERN to Fr\'{e}jus 
scenario & \cite{Campagne:2006yx} \\
Medium $\gamma$ & {\tt BB\_350.glb} & $\gamma=350$ green field scenario 
& \cite{Burguet-Castell:2005pa} \\
Variable $\gamma$ & {\tt BBvar\_WC.glb} & Variable $\gamma$ beta beam with water Cherenkov detector, $50 \lesssim \gamma \lesssim 500$ & \cite{Huber:2005jk} \\[0.2cm]
	& {\tt BBvar\_TASD.glb} & Variable $\gamma$ beta beam with totally active scint. detector (TASD), 
$100 \lesssim \gamma \lesssim 3\, 000$ & \cite{Huber:2005jk} \\[0.4cm]
\multicolumn{4}{l}{\underline{Neutrino factories:}} \\
Standard & {\tt NFstandard.glb} & Standard neutrino factory, $50 \, \mathrm{kt}$ magnetized iron calorimeter, 
$E_\mu = 50 \, \mathrm{GeV}$ & \cite{Huber:2002mx} \\
Variable $E_\mu$ & {\tt NFvar.glb} & Variable neutrino factory, disapp. channels
{\em without} CID; $10 \, \mathrm{GeV} \lesssim E_\mu \lesssim 80 \, \mathrm{GeV}$ & \cite{Huber:2002mx,Huber:2006wb}  \\
Gold + Silver & {\tt NF\_GoldSilver.glb} & As {\tt NFvar.glb} 
plus 5~kt ECC detector for Silver Channel
measurement & \cite{Huber:2002mx,Huber:2006wb,Autiero:2003fu} \\
Hybrid detector & {\tt NF\_hR\_lT.glb} & As {\tt NFvar.glb}, but 
lower threshold and better energy resolution & \cite{Huber:2002mx,Huber:2006wb} \\
\hline
\end{tabular}
\end{center}
} % small
\mycaption{\label{tab:experiments} 
Pre-defined experiment prototypes coming with \GLOBESN : The columns represent the \AEDL\ filename, 
a short description, and the references in which they are originally used and 
discussed (except from minor modifications, such as a different implementation of 
the energy threshold function). 
%
IS THE GAMMA=350 OPTION REALLY GREEN-FIELD? I THOUGHT THAT THIS MAY BE THE MAXIMUM
ONE COULD GET OUT OF THE SPS WITH ACCELERATOR MODIFICATIONS? [WW]
}
\end{table}
